EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-06-01 02_install.tex
Listing overhaul Fine tune colors New keywords (python)

\noindent
The CMake configuration can be further tuned using the following variables:
\begin{center}
\begin{tabular}{ l|l|l } 
 \hline
  {\bf Option}               & {\bf Scope} & {\bf Value} \\
  \hline
  -D{\bf PREFIX}          & Install directory  & {\color{red} $\sim$/opt/EDIpack/TAG/PLAT/BRANCH} \\
  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{red}True}/{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG \\
 \hline
\end{tabular}
\end{center}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for either components are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

>>>>

\noindent
The CMake configuration can be further tuned using the following variables:
\begin{center}
\begin{tabular}{ l|l|l } 
 \hline
  {\bf Option}               & {\bf Scope} & {\bf Value (default in {\color{xkcdEmerald}green})}\\
  \hline
  -D{\bf PREFIX}          & Install directory  & {\color{xkcdEmerald} $\sim$/opt/EDIpack/TAG/PLAT/BRANCH} \\
  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{xkcdEmerald}False}\\
  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{xkcdEmerald}True}/{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}/{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}/TESTING/DEBUG \\
 \hline
\end{tabular}
\end{center}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for either components are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

### 2025-06-01 05_examples.tex
Listing overhaul Fine tune colors New keywords (python)

    #Perform self-consistency levaragin {\tt aux\_funx.py} procedures:
    Gmats = get_gloc(wm*1j       ,ed.xmu,HkNambu,Smats,axis="m")
    Weiss = dmft_weiss_field(Gmats,Smats)

>>>>

    #Perform self-consistency levaragin {\tt aux\_funx.py} procedures:
    Gmats = get_gloc(wm*1j,ed.xmu,HkNambu,Smats,axis="m")
    Weiss = dmft_weiss_field(Gmats,Smats)
